Model

### 2019-05-31 stats/model.Rmd
update model run comp
update model run comparison plot

sem_know_run_summary <- sem_know_run_iteration%>%
  group_by(run,item)%>%
  summarise(overall_int = estimate_mode(int),
            overall_slope = estimate_mode(slope))

@@

run_comp <- sem_know_run %>%
  left_join(expand.grid(
      age = unique(me_model_data$age),
      item = unique(me_model_data$familiar)), .) %>%
  mutate(sem_know_ci = plogis(int + slope * age),
         sem_know = plogis(overall_int + overall_slope * age)) %>%
  group_by(run,item, age) %>%
  summarise(sem_know = estimate_mode(sem_know), 
            sem_know_uci = hdi_upper(sem_know_ci),
            sem_know_lci = hdi_lower(sem_know_ci))

ggplot(run_comp, aes(x = age+2, y= sem_know, fill = run))+
  geom_line(size = 1, aes(col = run))+
  geom_ribbon(aes(ymin=sem_know_lci, ymax = sem_know_uci), alpha = .2)+
  ylab("Semantic knowledge")+
  xlab("Age")+
  ylim(0,1)+
  facet_wrap(~item)+
  theme_few()+
  scale_colour_solarized()+
  scale_fill_solarized()
```

>>>>

sem_know_run_summary <- sem_know_run_iteration%>%
  group_by(run,Chain,item)%>%
  summarise(overall_int = estimate_mode(int),
            overall_slope = estimate_mode(slope))

@@

run_comp <- sem_know_run %>%
  left_join(expand.grid(
      age = unique(me_model_data$age),
      item = unique(me_model_data$familiar)), .) %>%
  mutate(sem_know_ci = plogis(int + slope * age),
         sem_know = plogis(overall_int + overall_slope * age)) %>%
  group_by(run,Chain,item, age) %>%
  summarise(sem_know = estimate_mode(sem_know), 
            sem_know_uci = hdi_upper(sem_know_ci),
            sem_know_lci = hdi_lower(sem_know_ci))

ggplot(run_comp, aes(x = age+2, y= sem_know, fill = run, group = paste(run,Chain)))+
  geom_line(size = .3, aes(col = run))+
  geom_ribbon(aes(ymin=sem_know_lci, ymax = sem_know_uci), alpha = .1)+
  ylab("Semantic knowledge")+
  xlab("Age")+
  ylim(0,1)+
  facet_wrap(~item)+
  theme_few()+
  scale_colour_solarized()+
  scale_fill_solarized()

ggsave("../graphs/model_by_chain_run.pdf", width = 10, height = 8)
```
